Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments \tnoteref{t1}

### 2024-02-06 article/article.tex
c
update and Sims

\tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Quantile Regressions via Method of Moments with multiple fixed effects },
  pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
  pdfkeywords={Fixed effects, Linear heteroskedasticity, Location-scale
model, Quantile regression},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Quantile Regressions via Method of Moments with multiple fixed
effects \tnoteref{t1}}
\author[1]{Fernando Rios-Avila%
\corref{cor1}%
}
 \ead{friosavi@levy.org} 
\author[2]{Leonardo Siles%
%
}
 \ead{leonardosiles@hotmail.com} 
\author[3]{Gustavo Canavire-Bacarreza%
%
}
 \ead{gcanavire@worldbank.org}

@@

\begin{keyword}
    Fixed effects \sep Linear heteroskedasticity \sep Location-scale
model \sep 
    Quantile regression
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, interior hidden, enhanced, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Quantile regression (QR), introduced by \citet{koenkerbasset1978}, is an
estimation strategy used for modeling the relationships between
explanatory variables X and the conditional quantiles of the dependent
variable \(Q_y (\tau|x)\). Using QR one can obtain richer
characterizations of the relationships between dependent and independent
variables, by accounting for otherwise unobserved heterogeneity.

@@

In this framework, our paper expands on \citet{mss2019}, following some
of the suggestions by these authors regarding further research. First,
making use of the properties of generalized method of moments (GMM)
estimators, we derive various alternatives for the estimation of
standard errors based on the empirical influence functions of the
estimators. Second, we reconsider the application of Frisch-Waugh-Lovell
(FWL) theorem \citep[ and \citet{lovell1963}]{frishwaugh1933} to extend
the MSS estimator to allow for the inclusion of multiple fixed effects,
for example, individual and year fixed effects.

The rest of the paper is structured as follows: section 2 presents the
basic setup of the location-scale model described in \citet{he1997} and
\citet{zhao2000}, tying the relationship between the standard quantile
regression model and the location-scale model. It also revisits the
methodology of MSS, proposing alternative estimators for the standard
errors based on the properties of GMM estimators and the empirical
influence functions. It also shows that the FWL theorem can be used to
control for multiple fixed effects. Section 3 presents the results of a
small simulation study and section 4 illustrates the application of the
proposed methods with two empirical examples. Section 5 concludes.

\hypertarget{sec-method}{%
\section{Methodology}\label{sec-method}}

\hypertarget{sec-betas}{%
\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}}

@@

\begin{equation}\protect\hypertarget{eq-eq1}{}{Q_y(\tau|X) =X\beta(\tau)
}\label{eq-eq1}\end{equation}

This allows for nonlinearities in the effect of \(X\) on \(Y\) across
all values of \(\tau\). This formulation can also be related to a random
coefficient model, in which all coefficients are assumed to be some
nonlinear function of \(\tau\) where \(\tau\) follows a random uniform
distribution.

@@

\begin{equation}\protect\hypertarget{eq-eq2}{}{Q_y(\tau|X) =X\beta+X\gamma(\tau)
}\label{eq-eq2}\end{equation}

Here, the location parameters \(\beta\) are typically identified using a
linear regression model (as in \citet{mss2019}) or a median regression
(as in \citet{zhao2000}) and the scale parameters \(\gamma(\tau)\) can
be estimated using standard approaches.

@@

One insightful extension to the location-scale parameterizations
suggested by \citet{he1997}, \citet{cameron2005}, and \citet{mss2019} is
to assume that the data-generating process (DGP) can be written as a
linear model with a multiplicative heteroskedastic process that is
linear in parameters.\footnote{\citet{mss2019} also discuss a model
  where heteroskedasticity can be an arbitrary nonlinear function
  \(\sigma(x_i'\gamma)\), but develop the estimator for the linear case,
  i.e., when \(\sigma()\) is the identity function.}

\begin{equation}\protect\hypertarget{eq-eq4}{}{\begin{aligned}
y_i &=x_i'\beta+\nu_i \\
\nu_i &=\varepsilon_i \times x_i'\gamma 
\end{aligned}
}\label{eq-eq4}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq-eq5}{}{Q_y(\tau|X) =X\beta+Q_\varepsilon(\tau) \times X\gamma 
}\label{eq-eq5}\end{equation}

In this setup, the traditional quantile coefficients are identified as
the location model coefficients plus the scale model coefficients
moderated by the \(\tau_{th}\) unconditional quantile of the
standardized error \(\varepsilon\). For simplicity we will use
\(q(\tau)\) to denote \(Q_\varepsilon(\tau)\) in the rest of the paper.

\begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + q(\tau) \times \gamma 
}\label{eq-eq6}\end{equation}

While this specification imposes a strong assumption on the DGP, it has
two advantages over the standard quantile regression model. First,
because the location-scale model can be identified globally, with only a
single parameter (\(q(\tau)\)) requiring local estimation, this
estimation approach will be more efficient than the standard quantile
regression model (\citet{zhao2000}). Second, under the assumption that
\(X\gamma\) is strictly positive, the model will produce quantile
coefficients that do not cross.

Following MSS, the quantile regression model defined by
Equation~\ref{eq-eq5} can be estimated using a generalized method of
moments approach. And while it is possible to identify all coefficients
(\(\beta,\gamma, q(\tau)\)) simultaneously, we describe and use the
implementation approach advocated by MSS, which identifies each set of
coefficients separately.

@@

\begin{equation}\protect\hypertarget{eq-eq8}{}{\begin{aligned}
  |\nu_i| &=x_i'\gamma+\omega_i \\
   E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
  \end{aligned}
}\label{eq-eq8}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq-eq9}{}{\begin{aligned}
  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q(\tau)) \geq y_i \right) - \tau \right] &=0  \\
  E\left[  \mathbb{1}\left(   q(\tau) \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
  \end{aligned}
}\label{eq-eq9}\end{equation}

where one identifies the quantile of the error \(\varepsilon\) using
standardized errors \(\frac{y_i-x_i'\beta}{x_i'\gamma}\) or by finding
the values that identify the overall quantile coefficients
\(\beta(\tau)=\beta + \gamma q(\tau)\). Afterwards, the conditional
quantile coefficients are simply defined as the combination of the
location and scale coefficients.

\hypertarget{sec-se}{%
\subsection{Standard Errors: GLS, Robust, Clustered}\label{sec-se}}

@@

\begin{equation}\protect\hypertarget{eq-eq10}{}{\begin{aligned}
  E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
  E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
  E\left[  \mathbb{1}\left(   q(\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
  &=E[h_{3,i}]=0 
  \end{aligned}
}\label{eq-eq10}\end{equation}

@@

Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\tau) ]'\) the set of
coefficients that are identified by the moment conditions in
Equation~\ref{eq-eq10}, a just identified model, and the function
\(h_i\) is a vector function that stacks all the moments described in
Equation~\ref{eq-eq10} at the individual level. Then \(\hat\theta\)
follows a normal distribution with mean \(\theta\) and
variance-covariance matrix \(V(\theta)\) that is estimated as

@@

In this framework, the quantile regression coefficients, a combination
of the location-scale-quantile estimates, will follow a normal
distribution with mean
\(\beta(\tau) = \beta+\gamma q(\varepsilon | \tau)\) and
variance-covariance matrix equal to

@@

\begin{equation}\protect\hypertarget{eq-eqqtile}{}{\Xi = [ I(k), \hat q(\tau) \times I(k), \hat \gamma ]
}\label{eq-eqqtile}\end{equation}

@@

\begin{equation}\protect\hypertarget{eq-eqvcv}{}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
}\label{eq-eqvcv}\end{equation}

@@

For the specific case of quantile regressions through moments, the
influence functions for the location, scale, and quantile coefficients
are\footnote{The derivation of the influence functions can be found in
  the appendix.}

\begin{equation}\protect\hypertarget{eq-ifs}{}{\begin{aligned}
\lambda_i(\theta)&=
  \begin{bmatrix}
  \lambda_{i}(\beta) \\
  \lambda_{i}(\gamma) \\
  \lambda_{i}(q(\tau)) 
  \end{bmatrix} \\
\lambda_{i}(\beta)&=N (X'X)^{-1}  x_i ( x_i'\gamma) \times \varepsilon_i \\
\lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
\lambda_{i}(q(\tau))&=\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\tau))}
- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
-  q(\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
}\label{eq-ifs}\end{equation}

@@

\[\hat{V}_{robust}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\tau))' \\
 \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\tau))' \\
 \sum \lambda_i(q(\tau)) \lambda_i(\beta)' & \sum \lambda_i(q(\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\tau)) \lambda_i(q(\tau))' 
  \end{pmatrix}
\]

This estimator of standard errors should be robust to arbitrary
heteroskedasticity. However, because the location-scale specification
relies on the correct specification of the model heteroskedasticity,
large differences in standard errors compared to GLS-standard errors may
be an indication of misspecification of the model.

\hypertarget{clustered-standard-errors}{%
\subsubsection{Clustered Standard
Errors}\label{clustered-standard-errors}}

@@

\[\hat{V}_{clustered}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum_{g=1}^{N_G} S\lambda_i(\theta) S\lambda_i(\theta)'
  \end{pmatrix}
\]

@@

\hypertarget{gls-standard-errors}{%
\subsubsection{GLS Standard Errors}\label{gls-standard-errors}}

@@

\[\begin{aligned}
\tilde \lambda_{1,i}&=\tilde \lambda_{2,i}=N (X'X)^{-1}  x_i ( x_i'\gamma) \\  
\tilde \lambda_{3,i}&=x_i' \gamma  \\
 \psi_{i,1} &= \varepsilon_i \\
 \psi_{i,2} &= \tilde \varepsilon_i -1 \\
 \psi_{i,3} &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
-  q(\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
\]

@@

\[\hat{V}_{gls}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q(\tau)
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \hat\sigma_{11} \hat\Omega_{11} & \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{11} \hat\Omega_{13} \\
 \hat\sigma_{21} \hat\Omega_{21} & \hat\sigma_{22} \hat\Omega_{22} & \hat\sigma_{21} \hat\Omega_{23} \\
 \hat\sigma_{31} \hat\Omega_{31} & \hat\sigma_{32} \hat\Omega_{32} & \hat\sigma_{33} \hat\Omega_{33}
  \end{pmatrix}
\]

@@

This estimator of stand ard errors is equivalent to the one derived by
MSS using Theorem 3.

\hypertarget{multiple-fixed-effects-expanding-on-mss2019}{%
\subsection{\texorpdfstring{Multiple Fixed Effects: Expanding on
\citet{mss2019}}{Multiple Fixed Effects: Expanding on @mss2019}}\label{multiple-fixed-effects-expanding-on-mss2019}}

Using the setup described in the previous section, \citet{mss2019}
proposes an extension to the model proposed by \citet{he1997} that
enables the estimation of quantile regression models with panel data,
allowing for the inclusion of individual fixed effects. However, as the
authors suggest, the methodology can be generalized to allow for the
inclusion of multiple fixed effects. This type of analysis can be useful
when considering data such as employer-employee linked data
\citep{abowed2006} or teacher-student linked data
\citep{harrissass2011}. Or, in the most common case, allowing to control
for both individual and time fixed effects.

We return to the original model and now assume there are sets of
unobserved heterogeneity that are assumed to be constant across
observations, if they belong to common groups. In panel data, the groups
would be the individual fixed effects and the time fixed effects.
Without loss of generality, we can assume that the data-generating
process is as follows:

@@

where we assume \(x_{i}\) vary across groups \(g_1\) and \(g_2\) (and
thus are not collinear) and that \(\delta's\) and \(\zeta's\) are the
location and scale effects associated with groups fixed
effects.\footnote{We could just as well consider multiple sets of fixed
  effects.}

If the dimension of groups \(g_k\) is low, this model could be estimated
using a dummy inclusion approach following Section~\ref{sec-betas}, and
the standard errors obtained as discussed in Section~\ref{sec-se}.
However, if the dimensionality of \(g_k\) is high, the dummy inclusion
approach may not be feasible. A more feasible approach is to apply the
FWL theorem and partial out the impact of the group fixed effects on the
control variables \(x_{i}\), and the outcome of interest \(y_{i}\),
using a similar approach for the identification of \(\sigma(x)\). In the
case of unbalanced setups with multiple groups, the estimation involves
iterative processes for which various approaches have been suggested and
implemented (see for example, \citet{correia_feasible_nodate},
\citet{gaure2013}, \citet{rios2015}, among others).

@@

\hypertarget{simulation-evidence}{%
\section{Simulation Evidence}\label{simulation-evidence}}

@@

\hypertarget{illustrative-application}{%
\section{Illustrative application}\label{illustrative-application}}

@@

\caption{\label{tbl-tb1}Determinants of Government Surpluses: Individual
Fixed Effects}\tabularnewline

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

>>>>

\tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments },
  pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
  pdfkeywords={Fixed effects, Linear heteroskedasticity, Location-scale
model, Quantile regression},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Estimating Quantile Regressions with Multiple Fixed Effects
through Method of Moments \tnoteref{t1}}
\author[1]{Fernando Rios-Avila%
\corref{cor1}%
}
 \ead{friosavi@levy.org} 
\author[2]{Leonardo Siles%
%
}
 \ead{leonardo.siles@ucb.edu.bo} 
\author[3]{Gustavo Canavire-Bacarreza%
%
}
 \ead{gcanavire@worldbank.org}

@@

\begin{keyword}
    Fixed effects \sep Linear heteroskedasticity \sep Location-scale
model \sep 
    Quantile regression
\end{keyword}
\end{frontmatter}

\section{Introduction}\label{introduction}

Quantile regression (QR), introduced by \citet{koenkerbasset1978}, is an
estimation strategy used for modeling the relationships between
explanatory variables X and the conditional quantiles of the dependent
variable \(Q_y (\tau|x)\). Using QR one can obtain richer
characterizations of the relationships between dependent and independent
variables, by exploring how the variables relate along the entire
conditional distribution.

@@

In this framework, our paper expands on \citet{mss2019} in two ways.
First, making use of the properties of generalized method of moments
(GMM) estimators, we derive various alternatives for the estimation of
standard errors based on the empirical influence functions of the
estimators. Even if the model is correctly specified, robust standard
errors perform better than GLS standard errors due small violations of
the model assumptions due to sampling variability. Furthermore,
clustered standard errors may help to further account for typically
unobserved correlations across observations. Second, we reconsider the
application of Frisch-Waugh-Lovell (FWL) theorem \citep[ and
\citet{lovell1963}]{frishwaugh1933} to extend the MSS estimator and
allow for the inclusion of multiple fixed effects. This extension may be
useful for empirical analysis, as it is common to control for multiple
fixed effects such as individual and time fixed effects.

The rest of the paper is structured as follows: section 2 presents the
basic setup of the location-scale model described in \citet{he1997} and
\citet{zhao2000}, tying the relationship between the standard quantile
regression model and the location-scale model. It also revisits the
methodology of MSS, proposing alternative estimators for the standard
errors based on the properties of GMM estimators and the empirical
influence functions. It also shows that the FWL theorem can be used to
control for multiple fixed effects. Section 3 presents the results of a
small simulation study and section 4 illustrates the application of the
proposed methods with one empirical example. Section 5 concludes.

\section{Methodology}\label{sec-method}

\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}

@@

\begin{equation}\phantomsection\label{eq-eq1}{Q_y(\tau|X) =X\beta(\tau)
}\end{equation}

This allows for a linear effect of \(X\) on \(Y\), but that could vary
across values of \(\tau\).

@@

\begin{equation}\phantomsection\label{eq-eq2}{Q_y(\tau|X) =X\beta+X\gamma(\tau)
}\end{equation}

Here, the location parameters \(\beta\) are typically identified using a
linear regression model (as in \citet{mss2019}) or a median regression
(as in \citet{he1997} and \citet{zhao2000}) and the scale parameters
\(\gamma(\tau)\) can be estimated using standard approaches.

@@

One insightful extension to the location-scale parameterizations
suggested by \citet{he1997}, \citet{zhao2000}, \citet{cameron2005}, and
\citet{mss2019} is to assume that the data-generating process (DGP) can
be written as a linear model with a multiplicative heteroskedastic
process that is linear in parameters.\footnote{\citet{mss2019} also
  discuss a model where heteroskedasticity can be an arbitrary nonlinear
  function \(\sigma(x_i'\gamma)\), but develop the estimator for the
  linear case, i.e., when \(\sigma()\) is the identity function.}

\begin{equation}\phantomsection\label{eq-eq4}{\begin{aligned}
y_i &=x_i'\beta+\nu_i \\
\nu_i &=\varepsilon_i \times x_i'\gamma 
\end{aligned}
}\end{equation}

@@

\begin{equation}\phantomsection\label{eq-eq5}{Q_y(\tau|X) =X\beta+Q_\varepsilon(\tau) \times X\gamma 
}\end{equation}

In this setup, the traditional quantile coefficients are identified as
the location model coefficients plus the scale model coefficients
moderated by the \(\tau_{th}\) unconditional quantile of the
standardized error \(\varepsilon\). For simplicity we will use
\(q_\tau\) to denote \(Q_\varepsilon(\tau)\) in the rest of the paper.

\begin{equation}\phantomsection\label{eq-eq6}{\beta(\tau) = \beta + q_\tau \times \gamma 
}\end{equation}

While this specification imposes a strong assumption on the DGP, it has
two advantages over the standard quantile regression model. First,
because the location-scale model can be identified globally, with only a
single parameter (\(q_\tau\)) requiring local estimation, this
estimation approach will be more efficient than the standard quantile
regression model (\citet{zhao2000}). Second, under the assumption that
\(X\gamma\) is strictly positive, the model will produce quantile
coefficients that do not cross (\citet{he1997}).

Following MSS, the quantile regression model defined by
Equation~\ref{eq-eq5} can be estimated using a generalized method of
moments approach. And while it is possible to identify all coefficients
(\(\beta,\gamma, q_\tau\)) simultaneously, we describe and use the
implementation approach advocated by MSS, which identifies each set of
coefficients separately.

@@

\begin{equation}\phantomsection\label{eq-eq8}{\begin{aligned}
  |\nu_i| &=x_i'\gamma+\omega_i \\
   E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
  \end{aligned}
}\end{equation}

It should be noticed that the estimation of the standard errors (next
section) requires that the Scale component prediction \(x_i'\gamma\) is
strictly positive, because it represents the conditional standard
deviation of the error \(\nu_i\). Because this component is identified
using a linear model, some values for \(x_i'\gamma\) may be negative,
which will affect the estimation of the standard errors, as shown in the
simulation study.

@@

\begin{equation}\phantomsection\label{eq-eq9}{\begin{aligned}
  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q_\tau) \geq y_i \right) - \tau \right] &=0  \\
  E\left[  \mathbb{1}\left(   q_\tau \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
  \end{aligned}
}\end{equation}

where one identifies the quantile of the error \(\varepsilon\) using
standardized errors \(\frac{y_i-x_i'\beta}{x_i'\gamma}\) or by finding
the values that identify the overall quantile coefficients
\(\beta(\tau)=\beta + \gamma q_\tau\). Afterwards, the conditional
quantile coefficients are simply defined as the combination of the
location and scale coefficients.

\subsection{Standard Errors: GLS, Robust, Clustered}\label{sec-se}

@@

\begin{equation}\phantomsection\label{eq-eq10}{\begin{aligned}
  E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
  E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
  E\left[  \mathbb{1}\left(   q_\tau\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right]  &=E[h_{3,i}]=0 
  \end{aligned}
}\end{equation}

@@

Call \(\theta=[ \beta' \ \ \gamma' \ \ q_\tau ]'\) the set of
coefficients that are identified by the moment conditions in
Equation~\ref{eq-eq10}, a just identified model, and the function
\(h_i\) is a vector function that stacks all the moments described in
Equation~\ref{eq-eq10} at the individual level. Then \(\hat\theta\)
follows a normal distribution with mean \(\theta\) and
variance-covariance matrix \(V(\theta)\) that is estimated as

@@

In this framework, the quantile regression coefficients, a combination
of the location-scale-quantile estimates, will follow a normal
distribution with mean \(\beta(\tau) = \beta+\gamma q_\tau\) and
variance-covariance matrix equal to

@@

\begin{equation}\phantomsection\label{eq-eqqtile}{\Xi = [ I(k), \hat q_\tau \times I(k), \hat \gamma ]
}\end{equation}

@@

\begin{equation}\phantomsection\label{eq-eqvcv}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
}\end{equation}

@@

For the specific case of quantile regressions via moments, the influence
functions for the location, scale, and quantile coefficients
are\footnote{The derivation of the influence functions can be found in
  the appendix.}

\begin{equation}\phantomsection\label{eq-ifs}{\begin{aligned}
\lambda_i(\theta)&=
  \begin{bmatrix}
  \lambda_{i}(\beta) \\
  \lambda_{i}(\gamma) \\
  \lambda_{i}(q_\tau) 
  \end{bmatrix} \\
\lambda_{i}(\beta)&=N (X'X)^{-1}  x_i ( x_i'\gamma) \times \varepsilon_i \\
\lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
\lambda_{i}(q_\tau)&=\frac{\tau-\mathbb{1}\big( q_\tau  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q_\tau)}
- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
-  q_\tau \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
}\end{equation}

@@

\[\hat{V}_{robust}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q_\tau
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q_\tau)' \\
 \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q_\tau)' \\
 \sum \lambda_i(q_\tau) \lambda_i(\beta)' & \sum \lambda_i(q_\tau)\lambda_i(\gamma)' & \sum \lambda_i(q_\tau) \lambda_i(q_\tau)' 
  \end{pmatrix}
\]

This estimator of standard errors may prove useful for two reasons.
First, this estimator would be robust to misspecification of the scale
model assumptions, and thus it could be used as an informal test for the
validity of the model assumptions when compared to the GLS-standard
error (Section~\ref{sec-gls}). Second, as shown in the simulation study,
this estimator performs better than GLS-standard errors even if the
model is correctly specified, because of problemes caused when
\(x\hat\gamma\) is not strictly positive.

\subsubsection{Clustered Standard
Errors}\label{clustered-standard-errors}

@@

\[\hat{V}_{clustered}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q_\tau
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \sum_{g=1}^{N_G} S\lambda_i(\theta) S\lambda_i(\theta)'
  \end{pmatrix}
\]

@@

\subsubsection{GLS Standard Errors}\label{sec-gls}

@@

\[\begin{aligned}
\tilde \lambda_{1,i}&=\tilde \lambda_{2,i}=N (X'X)^{-1}  x_i ( x_i'\gamma) \\  
\tilde \lambda_{3,i}&=x_i' \gamma  \\
 \psi_{i,1} &= \varepsilon_i \\
 \psi_{i,2} &= \tilde \varepsilon_i -1 \\
 \psi_{i,3} &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q_\tau  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q_\tau)} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
-  q_\tau \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
\end{aligned}
\]

@@

\[\hat{V}_{gls}
  \begin{pmatrix}
  \hat\beta \\
  \hat\gamma \\
  \hat q_\tau
  \end{pmatrix}
 = \frac{1}{N^2} 
 \begin{pmatrix}
 \hat\sigma_{11} \hat\Omega_{11} & \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{13} \hat\Omega_{13} \\
 \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{22} \hat\Omega_{22} & \hat\sigma_{23} \hat\Omega_{23} \\
 \hat\sigma_{13} \hat\Omega_{13} & \hat\sigma_{23} \hat\Omega_{23} & \hat\sigma_{33} \hat\Omega_{33}
  \end{pmatrix}
\]

@@

This estimator of standard errors is equivalent to the one derived by
MSS using Theorem 3. Empirically, the simulation study shows that this
estimator may severily over estimate the standard errors, even if the
model is correctly specified. This happens because the sample estimates
of the scale model coefficients may be negative or close to zero.

\subsection{\texorpdfstring{Multiple Fixed Effects: Expanding on
\citet{mss2019}}{Multiple Fixed Effects: Expanding on @mss2019}}\label{multiple-fixed-effects-expanding-on-mss2019}

Using the setup described in the previous section, MSS proposes an
extension to the model proposed by \citet{he1997} that enables the
estimation of quantile regression models with panel data, allowing for
the inclusion of individual fixed effects. However, the methodology can
also be generalized to allow for the inclusion of multiple fixed
effects. This type of analysis can be useful when considering data such
as employer-employee linked data \citep{abowed2006} or teacher-student
linked data \citep{harrissass2011}. Or, in the most common case,
allowing to control for both individual and time fixed effects.

We return to the original model and now assume there are sets of
unobserved heterogeneity that are constant across observations, if they
belong to common groups. Without loss of generality, we can assume that
the data-generating process is as follows:

@@

where we assume \(x_{i}\) vary across groups \(g_1\) and \(g_2\) (and
thus are not collinear) and that \(\delta's\) and \(\zeta's\) are the
location and scale effects associated with the groups fixed
effects.\footnote{We could just as well consider multiple sets of fixed
  effects.}

If the dimension of groups \(g_k\) is low, this model could be estimated
using a dummy inclusion approach following Section~\ref{sec-betas}, and
the standard errors obtained as discussed in Section~\ref{sec-se}.
However, if the dimensionality of \(g_k\) is high, the dummy inclusion
approach may not be computationally feasible. A more feasible approach
is to apply the FWL theorem and partial out the impact of the group
fixed effects on the control variables \(x_{i}\), and the outcome of
interest \(y_{i}\), and using a similar approach for the identification
of \(\sigma(x)\). In the case of unbalanced setups with multiple groups,
the estimation involves iterative processes for which various approaches
have been suggested and implemented (see for example,
\citet{correia_feasible_nodate}, \citet{gaure2013}, \citet{rios2015},
among others).

@@

\section{Simulation Evidence}\label{simulation-evidence}

@@

\section{Illustrative application}\label{illustrative-application}

@@

\caption{Determinants of Government Surpluses: Individual Fixed
Effects}\label{tbl-tb1}\tabularnewline

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}
